Coursera Project - Practical Machine Learning
========================================================
## Abstract
Ensamble of three models is trained in attempt to predict type of exercise
activity from set of parameters obtained from wearable tech. 
Three different models are tested and combination is used to as final predictor.

## Load caret library
```{r warning=FALSE}
library("caret")
```

## Load Data set (training)
```{r warning=FALSE}
raw_training <- read.csv(file="pml-training.csv")
raw_training$classe <- as.factor(raw_training$classe)
```
## Prepare Training set:
Following covariates will be used in training (other contain too many NAs to be 
of much use or lack any useful meaning)
- roll_belt, pitch_belt, yaw_belt
- gyros_belt_x, y and z
- accel_belt_x, y and z
- magnet_belt_x, y and z
- roll_arm, yaw_arm, pitch_arm
- total_accel_arm
- gyros_arm_x, y and z
- accel_arm_x, y and z
- magnet_arm_x_y and z
- roll_dumbbell, pitch_dumbbell, yaw_dumbbell
```{r warning=FALSE}
training <- raw_training[, which(names(raw_training) %in% c("roll_belt","pitch_belt","yaw_belt","gyros_belt_x","gyros_belt_y","gyros_belt_z","accel_belt_x","accel_belt_y","accel_belt_z","magnet_belt_x","magnet_belt_y","magnet_belt_z","roll_arm","yaw_arm","pitch_arm","total_accel_arm","gyros_arm_x","gyros_arm_y","gyros_arm_z","accel_arm_x","accel_arm_y","accel_arm_z","magnet_arm_x","magnet_arm_y","magnet_arm_z","roll_dumbbell","pitch_dumbbell","yaw_dumbbell","classe"))]
training$classe <- as.factor(training$classe)
```
## Perform training
For this project, 3 models are trained (gradient boosting machine (gbm), random forest (rf) and flexible discriminant analysis (fda)

Each model is trained on 10% of training set and models are evaluated on test set composed from rest of the training set
Note: training set had to be reduced to allow training in reasonable time frame with avaliable hardware, it is expected this is not optimal size of training set.
```{r cache=TRUE, warning=FALSE}
train50 <- createDataPartition(y=training$classe, p=0.10,list=FALSE)
modeltrain <-training[train50,]
modelcomparison <- training[-train50,]
```
###Training RF:
```{r cache=TRUE, warning=FALSE}
rfmodel <- train(classe ~ ., data=modeltrain,method="rf",prox=TRUE,verbose=FALSE)
```
###Summary: 
```{r warning=FALSE}
rfmodel
```
###Training GBM:
```{r cache=TRUE, warning=FALSE}
gbmmodel <- train(classe ~ ., data=modeltrain,method="gbm",verbose=FALSE)
```
###Summary:
```{r}
gbmmodel
```
###Training FDA:
```{r cache=TRUE, warning=FALSE}
fdamodel <- train(classe ~., data=modeltrain,method="fda")
```
###Summary: 
```{r}
fdamodel
```
## Model accuracy calculation
```{r warning=FALSE}
predrf <- predict(rfmodel,modelcomparison)
predfda <- predict(fdamodel,modelcomparison)
predgbm <- predict(gbmmodel,modelcomparison)
trainpredrf <- predict(rfmodel,modeltrain)
trainpredfda <- predict(fdamodel,modeltrain)
trainpredgbm <- predict(gbmmodel,modeltrain)
```
## Models accuracy:
### RF model accuracy:
- training set accuracy = `r sum(trainpredrf==modeltrain$classe)/nrow(modeltrain)*100` %
- model comparison set accuracy = `r sum(predrf==modelcomparison$classe)/nrow(modelcomparison)*100` %


### FDA model accuracy: 
- training set accuracy = `r sum(trainpredfda==modeltrain$classe)/nrow(modeltrain)*100` %
- model comparison set accuracy = `r sum(predfda==modelcomparison$classe)/nrow(modelcomparison)*100` %


### GMB model accuracy:
- training set accuracy = `r sum(trainpredgbm==modeltrain$classe)/nrow(modeltrain)*100` %
- model comparison set accuracy = `r sum(predgbm==modelcomparison$classe)/nrow(modelcomparison)*100` %

## Assemble models into combined predictor
Prediction is performed with each model and new model is trained to combine predictors
```{r cache=TRUE, warning=FALSE}
predDF <- data.frame(predrf,predgbm,predfda,classe=modelcomparison$classe)
combmodel <- train(classe ~ ., data=predDF,method="fda")
combinedpred <- predict(combmodel,predDF)
combmodel
```
- combined model training set accuracy = `r sum(combinedpred==predDF$classe)/nrow(predDF)*100` %
